The Lipid Interactome Repository

### 2025-02-27 IndividualStudies/AT_2025.qmd
Adding GO analysis to DH_2017
new links on index.qmd, reduced library redundancy
Updated the GO box, made uniform across all pages

@@

:::{.border}

@@

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)

>>>>

[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

@@

@@

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
:::

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

### 2025-02-27 IndividualStudies/DH_2017.qmd
new links on index.qmd, reduced library redundancy
Updated the GO box, made uniform across all pages

## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(stringr)
library(pheatmap)
library(here)
library(heatmaply)
library(ggvenn)
library(scales)

@@

```{r, echo=FALSE, warning=FALSE}

DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)

>>>>

## intitialize libraries
library(here)

@@

## Gene Ontology Analysis

**In beta: GO analysis still under development**

[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

#### Cell Compartment

<iframe src="/IndividualStudies/GO_plots/DH_2017_CC_DOTPLOT.html" width="100%" height="500px"></iframe>

#### Molecular Function

<iframe src="/IndividualStudies/GO_plots/DH_2017_MF_DOTPLOT.html" width="100%" height="500px"></iframe>

#### Biological Process

<iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>
:::

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

:::{.border}
```{r Building Datatable, echo=FALSE, warning=FALSE}
DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)

### 2025-02-27 IndividualStudies/SF_2024.qmd
Updated the GO box, made uniform across all pages

(MF CNET plot failed in production)
:::

@@

@@

>>>>

(MF CNET plot failed in production)

@@

(BP CNET plot failed in production)

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

### 2025-02-27 LipidProbe/1-10_FattyAcid.qmd
Updated the GO box, made uniform across all pages

::: {.panel-tabset}

@@

(CC CNET plot failed in production)
:::

@@

(BP CNET plot failed in production)
:::
:::

>>>>

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

@@

(CC CNET plot failed in production)

@@

(BP CNET plot failed in production)
:::

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

### 2025-02-27 LipidProbe/8-3_FattyAcid.qmd
Trying to fix the dotplot framing on mobile, not much luck yet
Updated the GO box, made uniform across all pages

---
title: "Trifunctional 8-3 Fatty Acid"
crossref: 
  ref-hyperlink: true # (default is true)
prefer-html: true
html: default
---

@@

:::{.border}

@@

:::{.border}

<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

>>>>

---
title: "Trifunctional 8-3 Fatty Acid"
prefer-html: true
html: default
---

@@

(CC CNET plot failed in production)

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

### 2025-02-27 StudyInformation_includes/AT_2025_include.qmd
minor changes to study info
Updated the GO box, made uniform across all pages

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
</span>

@@

>>>>

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PA.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidylethanolamine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
</span>

@@

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| PA    | 60 min | 5 min  | 15 min | 5 min  |
| PE    | 60 min | 5 min  | 15 min | 5 min  |
